Species-specific effects of the Urban Heat Island on tree growth across Berlin

### 2021-09-15 analysis/paper/paper.Rmd

---
title: "Species-specific effects of the Urban Heat Island on tree growth across Berlin"
author:
  - Alexander G. Hurley$^{a *}$, Ingo Heinrich$^a$, ...
  - $^a$ *Geoforschungszentrum Potsdam, Section 4.3, Germany*
  - "* Corresponding author: hurley@gfz-potsdam.de"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output: 
    bookdown::html_document2:
      fig_caption: yes
      toc: true
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      toc: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
bibliography: 
  - uhi_references.bib
  - 04_gfz_uhi.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  **This document outlines the rationale for an analysis of tree growth (potential) and its relationship with the Urban Heat Island (UHI) effect in Berlin using an extensive, publicly available data set. It introduces preliminary results and provides an outlook for up-coming and potential work.**
keywords: |
  Uferbaeume; Anlagenbaeume; Strassenbaeume; 
highlights: |
  We will see. 
---

@@

```{r dsources-tab}

@@

             caption = caption,
             caption.short = caption,
             format = "latex",
             # col.names = c("Subject/Relevance",
             #              "Desc.",
             #              "Type",
             #              "Obsv. (n)",
             #              "Resolution (m)",
             #              "Source")
             escape = FALSE)

@@

- Temperature, environmental and urban controls on tree growth  
	+ Intra specific differences
	+ Sensitive trees in hot spots
	+ Temporal dynamics  
	+ Validity and limitations  
- Implications:  
  + Policy / planning:  
    - tree species
	  - Increase temporal coverage and accuracy  
		- which trees to prioritize for measurement campaigns  
		- Supplement species matrix etc. with these analyses  
  + Open data important --> drives innovation

>>>>

---
title: "Species-specific effects of the Urban Heat Island on tree growth across Berlin"
author:
  - Alexander G. Hurley$^{a *}$, Ingo Heinrich$^a$, ...
  - $^a$ *Geoforschungszentrum Potsdam, Section 4.3, Germany*
  - "* Corresponding author: hurley@gfz-potsdam.de"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output: 
    bookdown::html_document2:
      fig_caption: yes
      toc: true
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      toc: yes
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage[normalem]{ulem}
bibliography: 
  - uhi_references.bib
  - 04_gfz_UHI.bib
  - 07_phenoTram.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  **This document outlines the rationale for an analysis of tree growth (potential) and its relationship with the Urban Heat Island (UHI) effect in Berlin using an extensive, publicly available data set. It introduces preliminary results and provides an outlook for up-coming and potential work.**
keywords: |
  Uferbaeume; Anlagenbaeume; Strassenbaeume; 
highlights: |
  We will see. 
---

@@

```{r dsources-tab, eval = TRUE}

@@

             caption = caption,
             caption.short = caption,
             format = "latex",
             # col.names = c("Subject/Relevance",
             #              "Desc.",
             #              "Type",
             #              "Obsv. (n)",
             #              "Resolution (m)",
             #              "Source")
             escape = FALSE) %>% 
      kableExtra::landscape()

@@

1. Temperature, environmental and urban controls on tree growth  
	+ Intra specific differences
	+ Sensitive trees in hot spots
	+ Temporal dynamics  
	+ Validity and limitations

2. Implications:  
  + Policy / planning:  
    - tree species
	  - Increase temporal coverage and accuracy  
		- which trees to prioritize for measurement campaigns  
		- Supplement species matrix etc. with these analyses  
  + Open data important --> drives innovation
